Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-10-20 papers/thesis-kirstie/thesis.tex
some more edits

\noindent I. Introduction

@@

Schmidt applied his Soft Fundamental Measure Theory to various fluids with soft repulsive 
and soft attractive potentials, and developed an erf model for 
spheres with steep, short-range soft repulsive potentials~\cite{schmidt2000fluid}. In this paper, 
Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]
\newline
\newline
\noindent IIA. Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)

@@

\begin{figure}[h!]
    \centering
    %\includegraphics[height=3.5cm]{TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

The WCA potential is not well suited for implementing Density Functional Theory.  Therefore, an erf potential which closely approximates the WCA potential at temperatures of interest will be used instead of the WCA potential. The erf potential is given by 
\begin{equation}
	{V_{erf}=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}
\end{equation} 
where the parameter $\alpha$ is derived by setting the erf potential equal to the WCA potentail when r equals $\alpha$ 
\begin{displaymath}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{displaymath} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation} 
The parameter $\Xi$ is derived by matching the slope of the erf potential to the slope of the WCA potential at r=$\alpha$:
\begin{displaymath}{\frac{dV_{erf}(r=\alpha)}{dr}=\frac{dV_{WCA}(r=\alpha)}{dr}}\end{displaymath} 
and is given by: 
\begin{equation}
	{\Xi=\frac{\alpha}{6\sqrt{\pi}\left(\sqrt{\frac{\epsilon}{k_BT}\ln(2)}+\ln(2)\right)}}
\end{equation}

\noindent These conditions, along with V$_{erf}=$V$_{WCA}$ at $r=\alpha$, help fit the curve of the erf potential to the curve of the WCA potential.

@@

\[\]
\noindent IIB. The Theory of Freezing and Maxwell's Double Tangent Construction

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{T-n_Diagram.png}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify the number densities of the liquid and the solid during a phase transistion. The gray region is where the liquid and the solid coexist, and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure} 
%One way of implementing this practically is to determine what the Helmholtz free energy would be for both the liquid and solid phases at a particular temperature and density. Whichever phase has the lower Helmholtz free energy will be the phase that the substance will be in. 
%\[\]
\[\]
\noindent IIC. Classical Density Functional Theory (cDFT)

@@

\[{}\]
III. METHODS

@@

\noindent IV. Results and Discussion

@@

\noindent V. Conclusion

>>>>

\section I. Chapter 1 - Introduction

@@

Schmidt applied his Soft Fundamental Measure Theory to various fluids with soft repulsive 
and soft attractive potentials, and developed an erf model for 
spheres with steep, short-range soft repulsive potentials~\cite{schmidt2000fluid}. In this paper, 
Density Functional Theory (DFT) will be used to predict the freezing of a 
Weeks-Chandler-Anderson model fluid by applying SFMT with Schmidt's proposed 
erf model to form the functional for the excess Helmholtz free energy. 
%for generating the weight funcions, and Tarazona's tensor functional. 
Results will be compared to those generated from Monte-Carlo simulations.
%\[{}\]
\newline
\newline
\section{Chapter 2 - Theory}
\subsection{Model Fluids and the Weeks-Chandler-Anderson Fluid (WCA)}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=3.5cm]{TwoSpheres.pdf} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure}

The WCA potential is not well suited for implementing Density Functional Theory.  
Therefore, an erf potential which closely approximates the WCA potential at temperatures 
of interest will be used instead of the WCA potential. The erf potential is given by 
\begin{equation}
	{V_{erf}=-k_BT\ln\left[\frac{1}{2}\left(\operatorname{erf}\left(\frac{r-\alpha}{\Xi}\right)+1\right)\right]}
\end{equation} 
where the parameter $\alpha$ is derived by setting the erf potential equal to the WCA 
potentail when r equals $\alpha$ 
\begin{displaymath}{V_{erf}(r=\alpha)=V_{WCA}(r=\alpha)}\end{displaymath} 
and is given by 
\begin{equation}\label{alphaT}
	{\alpha=\sigma\left(\frac{2}{1+\sqrt{\frac{k_BT}{\epsilon}\ln(2)}}\right)^\frac{1}{6}}
\end{equation}

%Deleted old Xi method
%move 3-9 to methods

@@

\[\]
\subsection{The Theory of Freezing and Maxwell's Double Tangent Construction}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{T-n_Diagram.png}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify the number densities of the liquid and the solid during a phase transistion. The gray region is where the liquid and the solid coexist, and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure} 
%One way of implementing this practically is to determine what the Helmholtz free energy would be for both the liquid and solid phases at a particular temperature and density. Whichever phase has the lower Helmholtz free energy will be the phase that the substance will be in. 
%\[\]
\[\]
\subsection{Classical Density Functional Theory (cDFT)}

@@

\[{}\]
\section{Chapter 3 - Methods}

@@

\section{Chapter 4 - Results and Discussion}

@@

\section{Chapter 5 -  Conclusion}
